---
title: "Association Analysis"
author: "Alex"
date: "15/07/2021"
output:
  pdf_document: default
  html_document: default
---
# Associative Analysis



# Loading in our Library

```{r}
# Loading the arules library
#
library(arules)
```


# Loading in our data set
```{r}
# we will require while working with models of association rules
# ---
# 
path <-"http://bit.ly/SupermarketDatasetII"

Transactions<-read.transactions(path, sep = ",")
Transactions
```

# Verifying the object's class

```{r}

class(Transactions)
```

# Previewing our first 5 transactions
```{r}

#
inspect(Transactions[1:5])
```

# Generating a summary of the transaction dataset

```{r}

summary(Transactions)
```

# Exploring the frequency of some articles 
```{r}
itemFrequency(Transactions[, 8:10],type = "absolute")
round(itemFrequency(Transactions[, 8:10],type = "relative")*100,2)
```
# Producing a chart of frequencies and fitering 

```{r}

par(mfrow = c(1, 2))

# plot the frequency of items
itemFrequencyPlot(Transactions, topN = 10,col="darkgreen")
itemFrequencyPlot(Transactions, support = 0.1,col="darkred")
```
# Building a model based on association rules

```{r}

rules <- apriori (Transactions, parameter = list(supp = 0.001, conf = 0.8))
rules

```



# Showing the summarry of our model
```{r}
 
summary(rules)
```

# Observing rules built in our model
```{r}

inspect(rules[1:5])


```

# Sorting by an increase in confidence
```{r}

rules<-sort(rules, by="confidence", decreasing=TRUE)
inspect(rules[1:5])

```



# Conclusion
## From the above results, we can clearly state that people who buy french fries, mushroom cream sauce, pasta are 100% likely to buy an escalope.
## From the above results, we can clearly state that people who buy ground beef, light cream are 100% likely to buy milk.

