---
title: "Dimensionality Reduction"
author: "Alex"
date: "16/07/2021"
output:
  pdf_document: default
  html_document: default
---

# IMPORTING OUR DATASET
```{r}

path<-"http://bit.ly/CarreFourDataset" 

Dataset<-read.csv(path, sep = ",", dec = ".",row.names = 1)

head(Dataset)
```
```{r}
feature <- Dataset
library(dplyr)
```





# Label encoding the categorical column Gender
```{r}

Dataset$Gender <- ifelse(Dataset$Gender == "Male",1,2)
table(Dataset$Gender)

```
# label encoding the customer type column
```{r}

Dataset$Customer.type <- ifelse(Dataset$Customer.type == "Member",1,2)
table(Dataset$Customer.type)

```
# label encoding the payment column
```{r}

Dataset$Payment <- as.numeric(Dataset$Payment)
table(Dataset$Payment)

```
# label encoding the product line column
```{r}
 
Dataset$Product.line <- as.numeric(Dataset$Product.line)
table(Dataset$Product.line)

```

# label encoding the branch column
```{r}

Dataset$Branch <- as.numeric(Dataset$Branch)
table(Dataset$Branch)

```


```{r}
data2 <- select(Dataset, c(2,3,5,6,7,8,9,11,13,14,15))
```


```{r}
head(data2)
```
```{r}
data2 <- data2[ , unlist(lapply(data2, is.numeric))]  
```


```{r}


pca <- prcomp(data2, center = TRUE, scale. = TRUE)
summary(pca)
```

##  PCA is not suitable for this data since some principal components do not convey most of the information of the data hence we can use tnse as an alternative method























